---
title: "Working with SNEE Intelligence Function templates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Working with SNEE Intelligence Function templates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is a work in progress. Feedback welcome.

### Creating a quarto presentation from SNEE template

There are basic templates stored within the SNEEstyle package which can be used to create documents and presentations.

The \code{SNEEstyle::SNEE_quarto_setup()} function can be used to move them into your project area.

The following code creates a html quarto presentation called "draft1" in the "reports" folder of a project.

```{r plainplot, warning=FALSE, message=FALSE, error=FALSE, eval = FALSE}
library(SNEEstyle)

SNEE_quarto_setup(type = "presentation", format = "html", file_path = "reports", file_name = "draft1")
```

This brings across all the files needed to create a SNEE IF themed presentation.

The presentation can then be edited as normal.
